---
title: "Boston Housing Exploration"
output: html_notebook
---


I Start by importing the necessary libraries to run my analysis. I will be using the Boston Housing data set, a popular dataset for modeling.

```{r}
library(tidyverse)
library(MASS)
data(Boston)
```

I use the head command to get a quick look at the data.

```{r}
head(Boston)
```

I import the DataExplorer library. This package has a lot of useful functions for EDA plotting and discovery. I start by using the command plot_histogram() which plots histograms of each numeric column.  Many of the variables are not normally distributed, including the target variable medv.

```{r}
library(DataExplorer)
plot_histogram(Boston)

```


The plot_correlation function from the DataExplorer package plots a correlation matrix from a dataframe.  I use it to look for highly correlation variables.  I am going use medv as my target variable. Their is a high negative correlation with lstat and a high positive correlation with rm

```{r}
library(plotly)
map_dfr(Boston, scale) %>% plot_correlation()

```

```{r}
plot_missing(Boston) 
```


```{r}
library(caret)
split = createDataPartition(Boston$medv, p = 0.7, list = F)
train = Boston[split,]
test = Boston[-split,]
```

```{r}
ctrl <- trainControl(method = "repeatedcv", repeats = 10)
plsFit <- train(
  medv ~ .,
  data = Boston ,
  trControl = ctrl,
  method = "pls",
  ## Center and scale the predictors for the training
  ## set and all future samples.
  preProc = c("center", "scale"),
  tuneLength = 10
)
```

```{r}
plot(varImp(plsFit))
```

```{r}
plsFit
```



```{r}
rfFit <- train(
  medv ~ .,
  data = Boston ,
  trControl = ctrl,
  method = "ranger",
  importance = "impurity",
  ## Center and scale the predictors for the training
  ## set and all future samples.
  preProc = c("center", "scale"),
  tuneLength = 10
)
```

```{r}
rfFit
```

```{r}
plot(varImp(rfFit))
```

```{r}
regFit <- train(
  medv ~ .,
  data = Boston %>% drop_na(),
  trControl = ctrl,
  method = "glmnet",
  family = "gaussian",
  ## Center and scale the predictors for the training
  ## set and all future samples.
  preProc = c("center", "scale"),
  tuneLength = 10
)
```

```{r}
regpred = predict(regFit, test)
RMSE(regpred, test$medv)
```
```{r}
par(mfrow = c(2,2))
plot(varImp(regFit))
```



```{r}
knnFit <- train(
  medv ~ .,
  data = Boston ,
  trControl = ctrl,
  method = "knn",
  family = "gaussian",
  ## Center and scale the predictors for the training
  ## set and all future samples.
  preProc = c("center", "scale"),
  tuneLength = 10
)
```

```{r}
knnFit
```


```{r}
treeFit <- train(
  medv ~ .,
  data = Boston ,
  trControl = ctrl,
  method = "rpart",
  ## Center and scale the predictors for the training
  ## set and all future samples.
  preProc = c("center", "scale"),
  tuneLength = 10
)
```

```{r}
treeFit
```
```{r}
treeFit <- train(
  medv ~ .,
  data = Boston ,
  trControl = ctrl,
  method = "",
  ## Center and scale the predictors for the training
  ## set and all future samples.
  preProc = c("center", "scale"),
  tuneLength = 10
)
```

```{r}

```

